HBots

### 2020-12-20 HBtos/article/articleHBots.tex
Trayendo modificaciones del informe en latex de HBots

            \draw [help lines] (0,0) grid (16,16);

@@

>>>>

@@

    \subsubsection*{Turno 4}
    %TURNO 4 
    \begin{center}
        \begin{tikzpicture}

            \path   (8,10)  node (a) [circle,draw] {A}
                    (5,9) node (b) [circle,draw] {B}
                    (11,9) node (c) [circle,draw] {C}
                    (4,8) node (d) [circle,draw] {D}
                    (6,8) node (e) [circle,draw] {E}
                    (10,8) node (f) [circle,draw] {F}
                    (12,8) node (g) [circle,draw] {G}
                    (3,7) node (h) [circle,draw] {H}
                    (5,7) node (i) [circle,draw] {I}
                    (7,7) node (j) [circle,draw] {J}
                    (9,7) node (k) [circle,draw] {K}
                    (11,7) node (l) [circle,draw] {L}
                    (13,7) node (m) [circle,draw] {M}
                    (3,6) node (n) [circle,draw] {N}
                    (5,6) node (o) [circle,draw] {O}
                    (7,6) node (p) [circle,draw] {P}
                    (9,6) node (q) [circle,draw] {Q}
                    (11,6) node (r) [circle,draw] {R}
                    (13,6) node (s) [circle,draw] {S};

            \draw[thick,red]  (node cs: name =a ) -- (node cs:name =b);
            \draw[thick,blue] (node cs: name =a ) -- (node cs:name =c);
            \draw[thick,red] (node cs: name =b ) -- (node cs:name =d);
            \draw[thick,blue] (node cs: name =b ) -- (node cs:name =e);
            \draw[thick,red] (node cs: name =c ) -- (node cs:name =f);
            \draw[thick,blue] (node cs: name =c ) -- (node cs:name =g);
            \draw[thick,blue] (node cs: name =d ) -- (node cs:name =h);
            \draw[thick,red] (node cs: name =e ) -- (node cs:name =i);
            \draw[thick,blue] (node cs: name =e ) -- (node cs:name =j);
            \draw[thick,red] (node cs: name =f) -- (node cs:name =k);
            \draw[thick,blue] (node cs: name =f ) -- (node cs:name =l);
            \draw[thick,red] (node cs: name =g ) -- (node cs:name =m);
            \draw[thick,blue] (node cs: name =h) -- (node cs:name =n);
            \draw[thick,blue] (node cs: name =i ) -- (node cs:name =o);
            \draw[thick,red] (node cs: name =j ) -- (node cs:name =p);
            \draw[thick,blue] (node cs: name =k ) -- (node cs:name =q);
            \draw[thick ,red] (node cs: name =l ) -- (node cs:name =r);
            \draw[thick,red] (node cs: name =m ) -- (node cs:name =s);

            \path   (5,10)  node (a) [] {\textcolor {blue}{\mbox{$\displaystyle \binom{0}{0}$ }}}
                    (4,9) node (b) [] {\textcolor {blue}{\mbox{$\displaystyle \binom{1}{0}$ }}}
                    (6,9) node (c) [] {\textcolor {blue}{\mbox{$\displaystyle \binom{1}{1}$ }}}
                    (3,8) node (d) [] {\textcolor {blue}{\mbox{$\displaystyle \binom{2}{0}$ }}}
                    (5,8) node (e) [] {\textcolor {blue}{\mbox{$\displaystyle \binom{2}{1}$ }}}
                    (7,8) node (f) [] {\textcolor {blue}{\mbox{$\displaystyle \binom{2}{2}$ }}}
                    (2,7) node (g) [] {\mbox{$\displaystyle \binom{3}{0}$ }}
                    (4,7) node (h) [] {\textcolor {blue}{\mbox{$\displaystyle \binom{3}{1}$ }}}
                    (6,7) node (i) [] {\textcolor {blue}{\mbox{$\displaystyle \binom{3}{2}$ }}}
                    (8,7) node (j) [] {\mbox{$\displaystyle \binom{3}{3}$ }}
                    (1,6) node (k) [] {\mbox{$\displaystyle \binom{4}{0}$ }}
                    (3,6) node (l) [] {\mbox{$\displaystyle \binom{4}{1}$ }}
                    (5,6) node (m) [] {\textcolor {blue}{\mbox{$\displaystyle \binom{4}{2}$ }}}
                    (7,6) node (n) [] {\mbox{$\displaystyle \binom{4}{3}$ }}
                    (9,6) node (o) [] {\mbox{$\displaystyle \binom{4}{4}$ }};

            \path   (5,10)  node (a) [circle,draw,fill= gray] {\mbox{1}}
                    (4,9) node (b) [circle,draw,fill= gray] {\mbox{1}}
                    (6,9) node (c) [circle,draw,fill= gray] {\mbox{1}}
                    (3,8) node (d) [circle,draw,fill= blue] {\mbox{1}}
                    (5,8) node (e) [circle,draw,fill= gray] {\mbox{2}}
                    (7,8) node (f) [circle,draw,fill= gray] {\mbox{1}}
                    (2,7) node (g) [circle,draw,fill= gray] {\mbox{1}}
                    (4,7) node (h) [circle,draw,fill= blue] {\mbox{3}}
                    (6,7) node (i) [circle,draw,fill= gray] {\mbox{3}}
                    (8,7) node (j) [circle,draw,fill= gray] {\mbox{1}}
                    (1,6) node (k) [circle,draw,fill= gray] {\mbox{1}}
                    (3,6) node (l) [circle,draw,fill= gray] {\mbox{4}}
                    (5,6) node (m) [circle,draw,fill= blue] {\mbox{6}}
                    (7,6) node (n) [circle,draw,fill= gray] {\mbox{4}}
                    (9,6) node (o) [circle,draw,fill= gray] {\mbox{1}}
                    (0,5) node (p) [circle,draw,fill= gray] {\mbox{1}}
                    (2,5) node (q) [circle,draw,fill= gray] {\mbox{5}}
                    (4,5) node (r) [circle,draw,fill= red] {\mbox{10}}
                    (6,5) node (s) [circle,draw,fill= gray] {\mbox{10}}
                    (8,5) node (t) [circle,draw,fill= gray] {\mbox{5}}
                    (10,5) node (u) [circle,draw,fill= gray] {\mbox{1}};

    \subsection*{Ecuacion 1} 
    \begin{equation*}
        \displaystyle \sum_{k = 0}^{n} \sum_{j = 0}^{n} \binom{j+k}{k}    
    \end{equation*}
